% ---------------------------------*- Latex -*---------------------------------
% Filename: conclusion.tex
% Description: 
% Author: Fabian Wermelinger
% Email: fabianw@student.ethz.ch
% Created: Thu Dec 15 20:23:54 2011 (+0100)
% Version: 
% Last-Updated: Thu Dec 15 23:10:34 2011 (+0100)
%           By: Fabian Wermelinger
%     Update #: 6
% -----------------------------------------------------------------------------
% conclusion.tex starts here
% -----------------------------------------------------------------------------

\section{Conclusion}
\label{sec:conclusion}

All in all our simulations showed some interesting phenomena and sensitivities
to different parameters which we are going to summerize in the
following. Through the project some interesting new questions arised while
others could not be sufficiently be answered.

As described in the previous sections the type of the network did not had a to
big influence on the results of our simulation. Perhaps were these quite
similar results for the different network types a result of the well connected
networks we used for most of our simulations. The biggest difference about the
random graph and small world network that our simulations showed was that for a
random graph the spread of opinions across different clusters was not as
predictable as for small world networks. This could be a result that not all
the nodes of a random graph have such a short connection as in a small world
network. Overall our simulations showed for different parameters that the
diffusion of opinions is in small world networks in principal better.

Section~\ref{sec:comparisontoreal} showed that there is a relation of the model
implemented in \matlab to a real world event.  In order to perform more event
specific simulations, parameter sets determined from data of the particular
event must be provided.  In general we conclude that the experiment and the
model behave closer to each other if the elements in $\mathcal{N}$ and
$\mathcal{S}_i$ \emph{increase}.  However, the number of elements in
$\mathcal{S}_i$ must still be significantly less than the number of elements in
$\mathcal{N}$.

The next step in developing the model would be to implement a probability which
takes into account that an agent might not know all of its direct and indirect
neighbors.  The weight of that probability should be on its \emph{indirect}
neighbors.  The agents threshold field was always uniformly distributed for all
simulated data.  It would be interesting to see the effect of other
distribution models and their impact on the simulation results.  For example, a
normal distribution might be an alternative.  A normal distribution might yield
similar results as discussed in
Section~\ref{sec:influencethresholddistribution} if there are too many agents
with thresholds that are not too distinct. 

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "master"
%%% End: 

% -----------------------------------------------------------------------------
% conclusion.tex ends here
% -----------------------------------------------------------------------------

